There once was a grid at ol' Carkeek

### 2016-03-17 Manuscript/carkeek_grid.tex
add to methods

\subsection*{Laboratory Methods}

\subsection*{Data Preparation (Bioinformatics)}

>>>>

\subsection*{Laboratory Methods}
The sequencing run consisted of 14 samples ('libraries') prepared using different index sequences ligated during library preparation.
Of these libraries, ten comprised of amplicons prepared using the 16S protocol reported above, and four comprised of amplicons prepared using a 12S protocol similar to that reported by (CITE PORT 2015).

Pooled libraries were sequenced on an Illumina NextSeq at the Stanford Center for Functional Genomics (machine ID: NS50061; run ID: 115; flowcell ID: H3LFLAFXX).

\subsection*{Data Preparation (Bioinformatics)}
We calculated rates of cross-library contamination by counting occurrences of primer sequences: 12S primer sequences appearing in a 16S library (and vice versa) indicate an error in the preparation or sequencing procedures.
